---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rdd)

incumbency <- read_csv('Lee(2007)_RDReplication.csv')

incumbency <- incumbency %>%
  select(DWinNxt, DemWin, DifDPct, ForgnPct, GovWkPct, BlackPct, UrbanPct,
         DWinPrv, YearElec, CDNumAtL)

```

Regression Discontinuity on Incumbency Effect (Lee, 2007)
--

DifDPct - significant
Congressional District Number - significant
Foreign Percentage - significant
Black Percentage - significant
Urban Percentage - significant
Previous Democrat Win - significant

Government Worker Percentage - not significant
Year Elected - not significant
--
Bad Control Variables would be Media Coverage

```{r RD}

reg1 <- glm(DWinNxt ~ DemWin, data=incumbency)
#DemWin = 0.721859

reg2 <- glm(DWinNxt ~ DemWin + DifDPct + CDNumAtL + ForgnPct +
            BlackPct + UrbanPct + DWinPrv, data=incumbency)
summary(reg2)
#DemWin = 0.6309649

reg3 <- glm(DWinNxt ~ DemWin + GovWkPct + YearElec, data=incumbency)
#DemWin = 0.8011271

sub_inc <- incumbency %>% filter(abs(DifDPct-0)<15)

reg4 <- glm(DWinNxt ~ DifDPct, data=sub_inc)
summary(reg4)

reg4 <- RDestimate(DWinNxt ~ DifDPct, data=sub_inc)
plot(reg4)

summary(incumbency)
```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
