---
title: "Homework 4"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(varhandle)
```

## R Markdown

DID with Card and Krueger (1993)

New Jersey is the treatment group
Pennsylvania is the control group

SHEET - store identifier
STATE - state

EMPFT - number of full time employees affected by minimum wage
EMPPT - number of part time employees affected by minimum wage
NMGRS - number of manages affected by minimum wage
WAGE_ST - starting wage may or may not decrease
INCTIME - time for increase may or may not take a longer time
FIRSTINC - increase in wage may or may not decrease
BONUS - bonus may or may not decrease
HRSOPEN - hours open may or may not decrease 

```{r DiD}

restaurant <- read_csv('Card & Krueger (1994) - dataset.csv')

restaurant <- restaurant %>%
  select(SHEET, STATE, CHAIN, PCTAFF, EMPFT, EMPFT2, EMPPT, EMPPT2,  
         NMGRS, NMGRS2, WAGE_ST, WAGE_ST2, INCTIME, INCTIME2,
         FIRSTINC, FIRSTIN2, HRSOPEN, HRSOPEN2)

rest_diff <- restaurant %>%
  mutate(DEMPPT = EMPPT2 - EMPPT, DEMPFT = EMPFT2 - EMPFT,
         DMGRS = NMGRS2 - NMGRS, DWAGE = WAGE_ST2 - WAGE_ST,
         DINC = INCTIME2 - INCTIME, DHRS = HRSOPEN2 - HRSOPEN,
         DFINC = FIRSTIN2 - FIRSTINC) %>%
  select(SHEET, STATE, CHAIN, DEMPPT, DEMPFT, DMGRS, DWAGE, DINC,
            DHRS, DFINC) %>%
  mutate(STATE = as.factor(STATE))


reg = lm(DEMPFT ~ STATE,data = rest_diff)
summary(reg)
plot(DWAGE~ STATE, data=rest_diff)
abline(reg)

reg = glm(DEMPFT ~ STATE + STATE*DEMPPT + STATE*DWAGE +
            STATE*DMGRS + STATE*DINC + STATE*DHRS + STATE*DFINC,
            data = rest_diff)

summary(reg)
ggplot(rest_diff, aes(x = CHAIN, y = DWAGE, fill=STATE)) +
  geom_bar(stat="identity", position = "dodge") +
  scale_fill_discrete(name="", breaks=c(0,1), labels=c("Pennsylvania","New Jersey"))

ggplot(rest_diff, aes(x = SHEET, y = DEMPFT, color=STATE)) +
  geom_point(stat="identity", position = "dodge") +
  stat_smooth(method="lm")


summary(reg)

#Y0 before the program start
#Y1 after the program start
#Gi = 1 Pennsylvania State = 0
#Gi = 0 New Jersey State = 1

```
